The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-06 paper.tex
update

We perform the integration in \Cref{gammaray-emissivity} on each cell over the range of incident photon energy between\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background radiation) and\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight)\
and over the range of CRe Lorentz factor\
to obtain the simulated IC emissivities.

>>>>

We perform the integration in \Cref{gammaray-emissivity} on each cell\
over the range of CRe Lorentz factor, and\
the range of incident photon energy between\
$\epsilon_{\text{min}}=1.13\times10^{-4}$ eV (cosmic microwave background radiation) and\
$\epsilon_{\text{max}}=13.59$ eV (optical starlight)\
to obtain the simulated IC emissivities.
